Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-16 paper/main.tex
rename rod length variable to match previous ref
change heterogeneity plot

\begin{equation}
    x(t) =
    \left\{\begin{array}{ll}
            x_0 \exp(\lambda (t-t_0)) & t\geq t_0\\
            x_0 & \text{ else}
    \end{array}\right.
\end{equation}

@@

\label{subsec:parameter-estimation-individual-treatment}
\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-individual.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-average.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.33\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/parameter-distribution.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \caption{
        % TODO use same y-axis across the plots
        (A) The subfigure shows the time-evolution of the rod-lengths for every individual
        bacterium.
        These growth curves are fitted individually with delayed exponential function.
        (B) The datapoints are created by averaging the rod-lengths shown in subfigure (A) and then
        fitted with an exponential function.
        The uncertainty band is the standard deviation of the averaged datapoints.
        (C) Blue dots show the combination of estimated growth rates and delays for individual
        bacteria while the orange dot corresponds to the average.
        Ellipses around the datapoints are taken from the uncertainty of the fits.
        Time is given in units of frames of the movie from which the data have been extracted.
    }
    \label{fig:estimated-growth-rates}
\end{figure}

>>>>

\begin{equation}
    l(t) =
    \left\{\begin{array}{ll}
            l_0 \exp(\lambda (t-t_0)) & t\geq t_0\\
            l_0 & \text{ else}
    \end{array}\right.
\end{equation}

@@

\label{subsec:parameter-estimation-individual-treatment}
\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.4\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-individual.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.4\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/growth-rates-distribution.pdf}%
        \node at (0, 1)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        % TODO use same y-axis across the plots
        (A) The subfigure shows the time-evolution of the rod-lengths for every individual
        bacterium.
        These growth curves are fitted individually with delayed exponential function.
        (B) The datapoints are created by averaging the rod-lengths shown in subfigure (A) and then
        fitted with an exponential function.
        The uncertainty band is the standard deviation of the averaged datapoints.
        (C) Blue dots show the combination of estimated growth rates and delays for individual
        bacteria while the orange dot corresponds to the average.
        Ellipses around the datapoints are taken from the uncertainty of the fits.
        Time is given in units of frames of the movie from which the data have been extracted.
    }
    \label{fig:estimated-growth-rates}
\end{figure}
